---
title: "Icon Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Icon Reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fontawesome)
library(gt)
```

The `fontawesome` package has `r vec_fmt_integer(length(fontawesome::fa_metadata()[["icon_names_full"]]))` icons. *That's a lot of icons!* This reference table lists them all in alphabetical order by the icon name. With a function like `fa()`, you can use **Icon Name**, and not the **Full Name**, for sake of simplicity. Not too many icons have variants (those that do have both the *Solid* and *Regular* forms) but if you prefer a specific form the **Full Name** can be used within `fa()`.

<hr />

```{r echo=FALSE}
fa_icons_vec <- c()

for (i in seq_len(nrow(fontawesome:::fa_tbl))) {

  icon_svg_i <- as.character(fontawesome::fa(fontawesome:::fa_tbl[i, ][["full_name"]]))
  fa_icons_vec <- c(fa_icons_vec, icon_svg_i)
}

fontawesome_table <-
  fontawesome:::fa_tbl |>
  dplyr::select(icon = name, label, icon_name = name, full_name) |>
  dplyr::mutate(icon = fa_icons_vec) |>
  gt() |>
  fmt_markdown(columns = icon) |>
  cols_label(
    icon = ""
  ) |>
  cols_label_with(fn = function(x) gsub("_", " ", x)) |>
  tab_style(
    style = list(
      cell_text(
        font = system_fonts(name = "monospace-code"),
        size = px(12)
      ),
      cell_borders(
        sides = c("l", "r"),
        color = "lightblue",
        style = "dotted",
        weight = px(1.5))
    ),
    locations = cells_body(columns = -icon)
  ) |>
  tab_style(
    style = css(position = "sticky", top = "-1em", `z-index` = 10),
    locations = cells_column_labels()
  ) |>
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(columns = icon)
  ) |>
  cols_align(align = "center", columns = icon) |>
  cols_width(
    icon ~ px(50),
    label ~ px(200),
    icon_name ~ px(200),
    full_name ~ px(230)
  ) |>
  opt_all_caps() |>
  opt_stylize(style = 6) |>
  tab_options(
    table.border.top.style = "hidden",
    column_labels.border.bottom.style = "hidden",
    container.height = px(490)
  )

fontawesome_table
```

<hr />

Data table published on `r gt::vec_fmt_datetime(Sys.time(), format = "EEEE, MMMM d, y 'at' h:mm a ('UTC')")`.
